\documentclass[a4paper]{report}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumitem}
\usepackage[sc]{mathpazo}
\linespread{1.05}         % Palladio needs more leading (space between lines)
\usepackage[T1]{fontenc}
\usepackage[margin=1.5in, marginparwidth=2in]{geometry}
\newenvironment{ex}[1]
    {\noindent{\large \bf Exercise #1.}}{\vspace{0.5cm}}

\begin{document}
\begin{ex}{1.3.2}
\begin{enumerate}[label=\alph*)]
\item Let $A = \{0\}$. Then $\inf A = \sup A = 0$.
\item Impossible. Let the set in question be $\{a_1, a_2, \dots, a_n\}$ and
  suppose $a_s \geq a_i$ for all $i$ (such an $s$ must exist because the set is
  finite). Then $a_s$ is the maximum of the set and hence the set has a supremum.
\item The set $\{\frac{1}{n} \mid n \in \mathbb{Z}\}$ does the trick.
\end{enumerate}
\end{ex}

\begin{ex}{1.3.3}
\begin{enumerate}[label=\alph*)]
\item Since $A$ is bounded below, $B \neq \varnothing$. Furthermore, since $A$
  is nonempty, $B$ must have an upper bound. By the Axiom of Completeness,
  $\sup B$ exists.

  Each $a \in A$ must be an upper bound for $B$ since $b \leq a$. Hence, by part
  ii) of the definition, $\sup B \leq a$ for each $a$, establishing $\sup B$ as
  a lower bound of $A$. Part i) of the definition says that for all lower bounds
  $b \in B$, $b \leq \sup B$. So, we conclude that $\sup B =
  \inf A$.

\item Part a) shows that any nonempty set that is bounded below has an infimum.
\end{enumerate}
\end{ex}

\begin{ex}{1.3.4}
\begin{enumerate}[label=\alph*)]
\item By the Axiom of Completeness, $\sup A_i$ exists for each $i$. 
Let $s_1 = \sup A_2$ and $s_2 = \sup A_2$ and suppose $s_1 \geq s_2$. For each
$a_1 \in A_1$ and $a_2 \in A_2$, $s_1 \geq a_1$ and $s_2 \geq a_2$. Hence, $s_1
\geq a_2$ and we conclude that $s_1$ is an upper bound of $A_1 \cup A_2$.

Let $b$ be an upper bound of $A_1 \cup A_2$. Then, $a_1 \leq b$ and $a_2 \leq
b$. So, $b$ is also an upper bound of $A_1$ and $A_2$. But $s_1 \leq b$ so $\sup
A_1 \cup A_2 = s_1$. 

Similarly, if $s_2 \geq s_1$, we have $ \sup A_1 \cup A_2 = s_2$. We conclude 
\begin{align*}
  \sup(A_1 \cup A_2) = \max(\sup A_1, \sup A_2)
\end{align*}
In general,
\begin{align*}
 \sup\left(\bigcup_{k=1}^n A_k\right) = \max(\sup A_1, \dots, \sup A_n)
\end{align*}
This can be proved by induction on $k$, with the base case ($k = 1$) being
trivial to prove and the inductive step following directly from part a) (where
you have to use the fact that $\max (\max (x_1, \dots, x_n), x_{n+1}) = \max
(x_1, \dots, x_n, x_{n+1})$).
\item No, because an infinite union of bounded sets can result in an unbounded
  set, which has no supremum. For example, 
\begin{align*}
\bigcup_{k=1}^\infty \{ x \mid \abs{x} \leq k\} = \mathbb{R}
\end{align*}
\end{enumerate}
\end{ex}

\begin{ex}{1.3.7}
\item Part i) of the definition is satisfied by assumption. For part ii), let
  $b$ be an upper bound of $A$. Then, for all $a' \in A$, $a' \leq b$ and,
  crucially, $a \leq b$. Hence, $a = \sup A$.
\end{ex}

\begin{ex}{1.3.10}
\begin{enumerate}[label=\alph*)]
\item By the Axiom of Completeness, $c = \sup A$ exists. Furthermore, since $a <
  b$ for all $a \in A, b \in B$, we have that $c \leq b$. But
  $a \leq c$ by definition, so we're done.
\item First, we need to construct disjoint nonempty sets $A, B$ such that $A
  \cup B = \mathbb{R}$. Let $B = \{ x \mid x > e \text{ for all } e \in E\}$.
  Since $E$ is nonempty is bounded above by some $b$, $B$ is nonempty (namely,
  it must contain $b + 1$). Let $A = B^c = {\{ x \mid x \leq e \text{ for all } e
  \in E \}}$. 


  Now, for $a \in A, b \in B, e \in E$, we have $a \leq e$ and $b > e$. Hence,
  $a < b$ as required. By the Cut Property, there exists $c \in \mathbB{R}$ such
  that $a \leq c$ and $c \leq b$. From the definition of $A$, this means that
  for all $e \in E$, $e \leq c$ such that $c$ is an upper bound on $E$, 
  satisfying part i) of the definition of the supremum. Additionally, suppose
  $d$ is an upper bound on $E$. If $d \in A$, then $e \leq d$ and $d
  \notin B$, meaning that $d < b$. This requires that $d = c$: if $c < d$, then
  $a \not\leq c$ for all $a$. Otherwise, $d \in B$, from which it follows that
  $c \leq d.$ We conclude that $c = \sup E$.

\item Let $A = \{ x \in \mathbb{Q} \mid x < \sqrt{2} \}$ and $B = \{x \in
  \mathbb{Q} \mid x > \sqrt{2}\}$. Clearly, $A \cup B = \mathbb{Q}$ (since
  $\sqrt{2} \notin \mathbb{Q}$) and $a < b$
  for all $a \in A$, $b \in B$. By the Cut Property, there exists $c \in
  \mathbb{Q}$ such that for all $a \in A$, $b \in B$, $a \leq c$ and $b \geq c$.
  Since $A \cup B = \mathbb{Q}$ and $A$ and $B$ are disjoint, either $c \in A$
  or $c \in B$. If $c \in A$, then $1 < c < \sqrt{2}$ and
\begin{align*}
c < c + \frac{2 - c^2}{2}  < \sqrt{2} 
\end{align*}
But this means that there's a rational number (namely $c + (2 - c^2)/2$) in $A$ larger
than $c$, which is a contradiction. A similar argument can be made if $c \in B$.
\end{enumerate}
\end{ex}

\begin{ex}{1.3.11}
  \begin{enumerate}[label=\alph*)]
  \item True. Since $A$ and $B$ are nonempty and bounded, $\sup A$ and $\sup B$
    exist. Since $A \subseteq B$, $a \leq \sup B$ for all $a \in A$, i.e., $\sup
    B$ is an upper bound for $A$. Additionally, $\sup A \leq b$ for all
    upper bounds $b$ of $A$. Hence, $\sup A \leq \sup B$.

  \item True. Since $\sup A$ and $\inf B$ exist, $A$ and $B$ must be nonempty
    and bounded. Suppose there does not exist $c \in \mathbb{R}$ such that $a < c <
    b$ for all $a \in A, b \in B$. Then, there exists $a' \in A$ and $b' \in B$
    with $b' \leq a'$. (If $a' < b'$ then $a' < a' + (b'-a')/2 = (a' + b')/2 < b'$ so it must be the case
    that $b' \leq a'$.) But by assumption $a' \leq \sup A < \inf B \leq b'$,
    which is a contradiction.

  \item False. Let $A = B = \varnothing$, then the assumption trivially holds
    but neither $\sup A$ nor $\inf B$ exists.
  \end{enumerate}
\end{ex}

\begin{ex}{1.4.1}
  \begin{enumerate}[label=\alph*)]
    \item Let $a = {p}/{q}$ and $b = {m}/{n}$. Then $ab = (pm)/(qn)$. Since
      $\mathbb{Z}$ is closed under multiplication, $ab \in \mathbb{Q}$. Similar
      for $a + b$, given that $\mathbb{Z}$ is closed under addition.
    \item Suppose $a + t \in \mathbb{Q}$. Then,
      there exists $p, q \in \mathbb{Z}$ such that $a + t = p/q$. Now, since $a
      = m/n$ for some $m,n \mathbb{Z}$, we have $t = p/q - m/n = (np -
      mq)/(qn)$. But this contradicts the irrationality of $t$, so $a + t \in
      \mathbb{I}$. Similar argument for $at \in \mathbb{I}$.
    \item Nothing. By part (b), $1 - \sqrt{2}, \sqrt{2}/2 -1, \sqrt{2}/{2} + 1
      \in \mathbb{I}$. But $(1 - \sqrt(2) + \sqrt(2) = 1 \in \mathbb{Q}$ and
      $(\sqrt{2}/2 -1) + (\sqrt{2}/2 + 1) = \sqrt{2} \in \mathbb{I}$. Similarly,
      $\sqrt{2}\sqrt{2} \in \mathbb{Q}$ but $(\sqrt{2} + 1)\sqrt{2} = 2 +
      \sqrt{2} \in \mathbb{I}$. Hence, $\mathbb{I}$ is neither closed under
      addition nor multiplication.
  \end{enumerate}
\end{ex}

\begin{ex}{1.4.2}
  First, we show that $s$ is an upper bound of $A$. Let $a' \in A$ and suppose
  $a' > s$, which implies $a' - s > 0$. By assumption, $s + 1/n \geq a'$ for all
  $n \in \mathbb{N}$. By the Archimedean Property, there exists $n_0 \in
  \mathbb{N}$ such that $1/n_0 < a' - s$. But this implies $s + 1/n_0 < a'$,
  which is a contradiction. Hence, $s \geq a$ for all $a \in A$.

  Now, we want to show that $s$ is a least upper bound. Let $b$ be an upper
  bound for $A$. By assumption, $s - 1/n < b$ for all $n \in \mathbb{N}$ so $1/n
  > s - b$. Now, suppose $s > b$. Then $s - b > 0$ and so, by the Archimedean
  Property, there exists $n_0 \in \mathbb{N}$ with $1/n_0 < s - b$. But this is
  a contradiction, so $s \leq b$.
\end{ex}

\begin{ex}{1.4.3}
Suppose there exists $x \in \cap_{n=1}^{\infty}(0, 1/n)$. Then, $0 < x < 1/n$
for all $n \in \mathbb{N}$. But, by the Archimedean Property, there exists $n_0
\in \mathbb{N}$ such that $1/n_0 < x$. This is a contradiction, so
$\cap_{n=1}^{\infty}(0, 1/n) = \varnothing$.
\end{ex}

\begin{ex}{1.4.5}
By Theorem 1.4.3, there exists $r \in \mathbb{Q}$ with $a - \sqrt{2} < r < b -
\sqrt{2}$. Hence, $a < r + \sqrt{2} < b$. But, by Exercise 1.4.1 part (a), $r +
\sqrt{2} \in \mathbb{I}$, so we're done.
\end{ex}

\begin{ex}{1.4.7}
  Choose $n_0 \in \mathbb{N}$ large enough so that
  \[ \frac{1}{n_0} < \frac{\alpha^2 - 2}{2\alpha}\]
  Then
  \begin{align*}
  \alpha^2 - \frac{2 \alpha}{n_0} > \alpha^2 - (\alpha^2 - 2) = 2.
  \end{align*}
But this contradicts the fact that $\alpha$ is a least upper bound of $T$.
Hence, we conclude that $\alpha^2 = 2$.
\end{ex}

\begin{ex}{1.5.1}
Let $n_m = \min \left\{n \in \left(\mathbb{N} \setminus \cup_{i=1}^{m-1} n_i \right)
\mid f(n) \in A\right\}$ and let $g(m) = f(n_m)$. Now suppose $g(s) = f(n_s) = f
(n_t) = g(t)$ for some $s, t \in \mathbb{N}$. Because $f$ is 1-1, $n_s = n_t$.
But if $n_s = n_t$ then $s = t$ because if $s < t$ then $n_s \notin
\left(\mathbb{N} \setminus \cup_{i=1}^{t-1} n_i \right)$ and a similar argument
can be made for $t < s$. Hence, $g$ is 1-1. Additionally, $g$ is onto:
if $a \in A$, there exists some $k \in \mathbb{N}$ with $f(k) \in A$ because
$f$ is onto. But there there must be some $m'$ such that $k = n_{m'}$ and hence
$g(m') = f(k) = a$.
\end{ex}

\begin{ex}{1.5.2}
NIP is only true for closed intervals on $\mathbb{R}$ and not $\mathbb{Q}$
(since the proof relies on AoC).
\end{ex}

\begin{ex}{1.5.3}
  \begin{enumerate}[label=\alph*)]
  \item Suppose $A_1$ and $A_2$ are countable and let $B_2 = A_2 \setminus A_1$.
    Since $B_2 \subseteq A_2$, $B_2$ is countable or finite by Theorem 1.5.7.
    Additionally, $A_1 \cup A_2 = A_1 \cup B_2$. Let $f_1 : \mathbb{N}
    \rightarrow A_1$ be 1-1 and onto. If $B_2$ is finite, then $B_2 = \{b_1, b_2,
    \dots, b_s\}$ and we define
    \begin{align*}
      g(n) &= \begin{cases}
        b_n & \text{$n \leq s$} \\
        f_1(n - s) & \text{n > s}
              \end{cases}
    \end{align*}
   $g$ is 1-1: if $g(n) = g(m)$ then either $g(n), g(m) \in B_2$ or $g(n), g(m) \in A_1$
   because $A_1$ and $B_2$ are disjoint. In the former case, we have $b_n = b_m$
   and conclude $n = m$. In the later case, we have $f_1(n - s) = f_1 (m - s)$
   and have $n = m$ since $f$ is 1-1.

   $g$ is onto: If $x \in B_2$ there is some $n$ with $b_n = x$. Hence, $g(n) =
   x$. If $x \in A_1$ then the surjectivity of $f$ gives an $n$ with $f(n) = x$.
   But then $g(n + s) = f_1(n) = x$.

   If $B_2$ is countable with bijection $f_2: \mathbb{N} \rightarrow B_2$, define
   
   \begin{align*}
     g(n) &= \begin{cases}
       f_1(n/2) & \text{$n$ even} \\
       f_2((n - 1)/2) & \text{$n$ odd}
     \end{cases}
   \end{align*}

   $g$ is 1-1: if $g(n) = g(m)$ and $g(n),g(m) \in A_1$ we have $f_1(n/2) = f_2(m/2)$
   and conclude $n = m$. Otherwise, we have $f_2((n - 1)/2) = f_2((m - 1)/2)$
   and have $n = m$ by the injectivity of $f_2$.

   $g$ is onto: Suppose $x \in A_1$. By the surjectivity of $f_1$, we have $n
   \in \mathbb{N}$ with $f_1(n) = x$. Hence, $g(2*n) = f_1(n) = x$. For $x \in
   B_1$, we have some $n$ with $f_2(n) = x$ and have $g(2*n + 1) = f_2(n) = x$
   (since $2*n + 1$ is always odd).

   The more general statement follows by induction on $m$. The inductive step is
   essentially the proof above.
  \item Infinity isn't a number: induction can only be used to prove $\cup_{n=1}^k
    A_n$ is countable for any $k \in \mathbb{N}$.
  \item  Let $R_1$ be the set of integers appearing in the first row of the
    array, $R_2$ in the second, and so on.  Clearly, these sets are all disjoint
    and there are an infinite number of them. Additionally, we'll annotate each
    integer in each $R_i$ with its sequence number via a pairing. For example, $R_1
    = \{ (1, 1), (2, 3), (3, 6), (4, 10), \dots\}$.


    Let $f_i : \mathbb{N} \rightarrow A_i$ be a bijection for each $A_i$. We define our bijective function $g : \mathbb{N} \rightarrow
    \cup_{n=1}^{\inf}A_n$ as
    \begin{align*}
      g(n) = \begin{cases}
        f_1(s) & \text{if $(s, n) \in R_1$ for some $s \in \mathbb{N}$} \\
        f_2(s) & \text{if $(s, n) \in R_2$ for some $s \in \mathbb{N}$} \\
         & \vdots
      \end{cases}
    \end{align*}

  $g$ is 1-1: If $g(n) = g(m)$ then both $g(n),g(m) \in A_i$ for some $i$ since
  the $A_i$'s are disjoint. Hence, $g(n) = f_i(n) = f_i(m) = g(m)$. But each
  $f_i$ is 1-1, so $n = m$.

  $g$ is onto: Let $z \in \cup_{n=1}^{\inf}A_n$. Then there is some $i \in
  \mathbb{N}$ such that $z \in A_i$. But since $f_i$ is onto, there is a $n \in
  \mathbb{N}$ with $f_i(n) = z$. But since $(n, m) \in R_i$ this means that
  $g(m) = f_i(n) = z$. 
\end{enumerate}
\end{ex}
\begin{ex}{1.5.6}
  \begin{enumerate}[label=\alph*)]
    \item The collection $\{(n -1, n) \mid n \in \mathbb{N}\}$ works with
      bijective function $f$ given by $f(n) = (n-1, n)$.
    \item No such collection exists. By Theorem 1.4.3, for any $a, b \in
      \mathbb{R}$ with $a < b$ there is a $r \in \mathbb{Q}$ with $a < r < b$.
      Hence, in any non-empty interval $(a, b)$ we have $r \in (a, b)$. Since
      the collection consists of disjoint intervals, it is easy to construct a
      bijective function from $\mathbb{Q}$ to the collection. But $\mathbb{Q}$
      is countable, so by Exercise 1.5.5, the collection must also be countable.
  \end{enumerate}
\end{ex}

\begin{ex}{1.5.11}
  \begin{enumerate}[label=\alph*)]
  \item Define $h_g : A' \rightarrow B'$ as $g^{-1}$ restricted to $A'$. That
    is, $h_g(a') = b'$ if $g(b') = a'$. Such a $b' \in B'$ exists for all $a'
    \in A$ because $g$ maps $B'$ onto $A'$. $h_g$ is 1-1: if $h_g(a') = h_g(a'')$
    then there are some $b', b'' \in B'$ such that $g(b') = a'$ and $g(b'') =
    a''$.  Hence, $b' = h_g(a') = h_g(a'') = b''$ and we conclude that $a' =
    a''$. $h_g$ is also onto: if $b' \in B'$ then $h_g(g(b')) = b'$. (We're
    guaranteed $g(b') \in A'$ because $g$ maps $B'$ onto $A'$.)

    Define $h_f : A \rightarrow B$ as $f$ restricted to $A$. $h_f$ is onto and
    1-1 by assumption.

    Finally, define
    \begin{align*}
      h(x) &= \begin{cases}
        h_g & \text {if $x \in A'$}, \\
        h_f & \text {if $x \in A$}
              \end{cases}
    \end{align*}
    $h$ is clearly onto and 1-1.
  \item If $A_1 = \varnothing$, then $g$ is onto and we're done (since $Y \sim
    X$ implies $X \sim Y$). So, assume $A_1 \neq \varnothing$. We show $A_n \cap
    A_{n+1} = \varnothing$ for all $n \in \mathbb{N}$ by induction on $n$.

    Base case ($n = 1$): We need to show that $A_1 \cap A_2 = \varnothing$.
    $A_1 = X\setminus g(Y)$ and $A_2 = g(f(A_1)) = g(f(X \setminus g(Y)))$. $A_1$
    consists precisely of all the elements that are \emph{not} in $g$'s
    range--since $A_2 \subseteq g(Y)$ we conclude that $A_1 \cap A_2 =
    \varnothing$.

    Inductive step: Suppose $A_{k} \cap A_{k+1} = \varnothing$ for all $k < n$.
    Note that $f(A_k) \cap f(A_{k+1}) = \varnothing$: if $a_k
    \in A_k$ and $a_{k+1} \in A_{k+1}$ then $f(a_k) \neq f(a_{k+1})$ because $f$
    is 1-1 and $A_{k}, A_{k+1}$ are disjoint. Similarly, $g(f(A_k)) \cap
    g(f(A_{k+1})) = \varnothing$ because $g$ is 1-1. But $A_{k+1} = g(f(A_k))$
    and $A_{k+2} = g(f(A_{k+1}))$, so we're done.

    The fact that the collection $\{f(A_n) \mid n \in \mathbb{N}\}$ follows
    immediately by the fact that $f$ is 1-1.
  \item Observe that
   \begin{align*}
A' = X \setminus A = X \setminus \cup_{n=1}^{\infty} A_n &= 
     X \setminus \left(A_1 \cup (\cup_{n=2}^{\infty} A_n) \right) = X \setminus \left( (X \setminus g(Y))  \cup (\cup_{n=2}^{\infty} A_2)\right) \subseteq g(Y)
\end{align*}
because $X \setminus (X \setminus g(Y)) = g(Y)$. If $z \in A'$ then there
is no $n \in \mathbb{Z^{\geq}}$ such that $(gf)^n(a_1) = z$ for all $a_1 \in A_1$. Since $A' \subseteq
g(Y)$, there eixsts $b \in B$ with $g(b) = z$. What remains to be shown is that
$b \in B'$. Suppose $b \notin B'$. Then $b \in \cup_{n=1}^{\infty} f(A_n)$. But
$b = f ((gf)^n a_1)$ for some $a_1 \in A_1$ and $n_0 \in \mathbb{N^{\geq}}$, so $g(b) = (gf)^{n_0+1} (a_1) = z$,
which is a contradiction. We conclude that $b \in B'$ and thus that $g$ maps
$B'$ onto $A'$.
  \end{enumerate}
\end{ex}
\begin{ex}{1.6.1}
Suppose $(0,1)$ is uncountable. We'll show that $\mathbb{R}$ is uncountable by
proving the contrapositive: namely, if $\mathbb{R}$ is countable then $(0,1)$ is
countable. But $(0, 1) \subseteq \mathbb{R}$ so, by Theorem 1.5.7, $(0,1)$ is
countable. Now suppose $\mathbb{R}$ is uncountable. Consider the function 
\begin{align*}
f(x) = \frac{x - 1/2}{x(x - 1)}
\end{align*}
As in Example 1.5.4, a bit of calculus shows the above takes $(0, 1)$ to
$\mathbb{R}$ in a 1-1 fashion.
\end{ex}

\begin{ex}{1.6.2}
\begin{enumerate}[label=\alph*)]
\item $b_1 \neq a_{11}$ by definition.
\item $b_2 \neq a_{22}$ by definition. In general, $b_n \neq a_{nn}$ by
  definition, so $x \neq f(n)$ for all $n \in \mathbb{N}$.
\item $x$ cannot appear in the table by part (b), which contradicts that $f$ is
  bijective.
\end{enumerate}
\end{ex}
\begin{ex}{1.6.3}
\begin{enumerate}[label=\alph*)]
\item $b \neq \mathbb{Q}$. Every rational number is
  finite or it repeats: such a $b$ (namely a rational one) cannot differ in
  every place.
\item No. The constructed number consists only of 2's and 3's, so this
  particular point is irrelevant and we can be sure that the table doesn't
  contain an alternate representation of $b$.
\end{enumerate}
\end{ex}
\begin{ex}{1.6.4}
Any real number can be encoded as a sequence in $S$. (An inefficient encoding
could just encode each digit as a 10-digit sequence where, e.g., $1 =
(1,0,0,0,0,0,0,0,0)$, $2 = (1,2,0,0,0,0,0,0,0)$, etc.) Let $E$ be such an
encoding function (which clearly has inverse $E'$ and is bijective) and let $f : \mathbb{N} \rightarrow S$ be bijective. Then we
can construct a bijection $g: \mathbb{N} \rightarrow \mathbb{R}$: $g = f \circ E$.
\end{ex}

\begin{ex}{1.6.6}
\begin{enumerate}[label=\alph*)]
\item \phantom{x}
  \begin{center}
  \begin{tabular}[h]{ccc|ccc}
    $f(a)$ & $\rightarrow$ & $\{a\}$ & $f(a)$ & $\rightarrow$ & $\varnothing$ \\
    $f(b)$ & $\rightarrow$ & $\{b\}$ & $f(b)$ & $\rightarrow$ & $\{b\}$ \\
    $f(c)$ & $\rightarrow $& $\{c\}$ & $f(c)$ & $\rightarrow$ & $\{c\}$ 
  \end{tabular}
  \end{center}
\item $g(x) = \{x\}$
\item Because for all sets $A$, $P(A) > A$ since $2^n > n$ for all $n \in
  \mathbb{Z^{\geq}}$.
\end{enumerate}
\end{ex}

\begin{ex}{1.6.8}
  \begin{enumerate}[label=\alph*)]
\item Suppose $a' \in B$. Since $f(a') = B = \{ a \in A \mid a \notin f(a')\}$,
  $a' \notin B.$
\item Suppose $a' \notin B$.  Since $f(a') = B = \{ a \in A \mid a \notin f(a')\}$,
  $a' \in B.$
  \end{enumerate}
\end{ex}

\begin{ex}{1.6.9}
$P(\mathbb{N})$ consists of all subsets of $\mathbb{N}$. Such subsets may
alternatively be interpreted as real numbers in the interval $(0, 1)$: the set
$\{a_1, a_2,\dots\}$ corresponds to the decimal number $.a_1a_2\dots$ . Such an
encoding is clearly bijective, so we're done.
\end{ex}
\end{document}
